---
lang: fr
output: 
  weasydoc::hpdf_document_base:
    engine: "weasyprint"
    keep_html: true
    css: style.css
---

```{r echo = FALSE }
library(knitr)
library(kableExtra)
library(htmltools)
library(magrittr)
tagList(rmarkdown::html_dependency_font_awesome())
```

## Example 1

### Issue

If you want to use `kable()` function in a css chunk (i.e. with `:::`), the latter is not recognized as CSS chunk but as text :

:::{.red}

A table with `{kable}` and `html` format

```{r}
 data.frame(x = 1:5, y = 1:5) %>%
   kable(format = "html")
```

:::

### Solution

The solution is to use the `html` format with the `htmltools::HTML()` function

:::{.green}

A table with `{kable}` and `html` format and `htmltools::HTML()` function

```{r}
 data.frame(x = 1:5, y = 1:5) %>%
   kable(format = "html") %>%
  HTML()
```

:::

OR to use the `markdown` format

:::{.green}

A table with `{kable}` and `markdown` format

```{r}
 data.frame(x = 1:5, y = 1:5) %>%
   kable(format = "markdown")
```

:::


## Example 2

### Issue 1

If you want to insert icons in a table using `kable` with solution 1 from issue #11, it doesn't work with `html` format :

:::{.red}

A table with `{kable}`, icons and `html` format

```{r}
 data.frame(x = "<i class=\"fa fa-envelope\"></i>", 
            y = "test") %>%
  kable(format = "html") %>%
  HTML()
```

:::

### Solution

It works with `markdown` format

:::{.green}

A table with `{kable}`, icons and `markdown` format

```{r}
 data.frame(x = "<i class=\"fa fa-envelope\"></i>", 
            y = "test") %>%
  kable(format = "markdown")
```

:::

### Issue 2

But then, if you want to use package `{kableExtra}` to pimp your table, you can't as it supports only `html` (or latex) format

:::{.red}

A table with `{kable}`, icons, `{kableExtra}` and `markdown` format

```{r}
 data.frame(x = "<i class=\"fa fa-envelope\"></i>", 
            y = "test") %>%
  kable(format = "markdown") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

:::

